The Impact of Educational Expenses of New Coders

### 2021-04-25 outputs/paper/paper.Rmd
Edit text in paper.Rmd

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
#### Multiple regression analysis ####

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
#### Multiple regression analysis (by city population) ####
dfSmCity <-
  dfNewCoders %>%
  filter(CityPopulation == 0)

@@

Since two multiple linear regression models (Model 2 and 3) are used in the first group of regression models, I will check if multicollinearity exists in these regression models, using variance inflation factor (VIF) and tolerance. I will use the `car` package to calculate the value of VIF and tolerance for each model [@citeCar]. Also, I will identify how much each of the independent variables affects the dependent variable with the standardized regression coefficients (beta). the `QuantPsyc` package will be used to compute the beta value [@citeQuanPsy].

# Results
```{r, include=FALSE}
#### Beta ####
# TODO: create a bar plot to show which variable affects the most with Beta
```

>>>>

Since two multiple linear regression models (Model 2 and 3) are used in the first group of regression models, I will check if multicollinearity exists in these regression models, using variance inflation factor (VIF) and tolerance. I will use the `car` package to calculate the values of VIF and tolerance for each model [@citeCar]. Also, I will identify how much each of the independent variables affects the dependent variable with the standardized regression coefficients (beta). the `QuantPsyc` package will be used to compute the beta value [@citeQuanPsy].

# Results

## Results of Regression Model

All the regression models in the first group of the models had p-values of F-statistic lower than a significance level of 0.05 (see Table 4). And, each of the independent variables also had a p-value of less than 0.05 except for the SchoolDegree variable in Model 3. This can be interpreted that all the independent variables excluding the SchoolDegree variable have an impact on the response variable (MoneyForLearning), and the level of education (SchoolDegree) is not statistically significant on the response variable with holding all other variables. However, the SchoolDegree variable becomes statistically significant if the Gender and Age variables are excluded from the regression model.

```{r tabLinRegModel1, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
#### Linear regression models (Group 1) ####

@@

The second group of regression models to examine the effects of the population of the city where the programmers reside shows that all the models have statistically significant p-values of F-statistic except for Model 5, the model for the small city with less than 100,000 residents (see Table 5). In other words, beginner programmers' income affects the cost of their education to learn code; however, their income does not affect the cost when the model contains only observations from the small city.

```{r tabLinRegModel2, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
#### Linear regression models (Group 2) ####
dfSmCity <-
  dfNewCoders %>%
  filter(CityPopulation == 0)

@@
